---
title: "mlr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mlr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

We have to download this package from the github and get the vignettes. Simutaneously, we can use the library to call the function.
```{r setup}
library(mlrmodel)
```

(1) Part I
First, we use the virtual data to fit a multiple linear regression model. We have to create a data by ourselves.
```{r}
n = 50
x1 = rnorm(n)
x2 = rnorm(n)
x3 = rnorm(n)
x = cbind(x1, x2, x3)
y = 4 + 3 * x1 + 2 * x2 - 1.5 * x3 + rnorm(n)
```

Then we fit a multiple regression model and get the coefficients of each variables.
```{r}
md1 = lrm(y, x)
print(md1$smry[, "beta"])
```

We get the partial SSE for each varibles.
```{r}
print(md1$smry[, "partial sse"])
```

We get the se(beta_hat).
```{r}
print(md1$smry[, "se beta_hat"])
```

We get the t-value for each varibles.
```{r}
print(md1$smry[, "t value"])
```

We get the p-value for each varibles and see whether they are significant.
```{r}
print(md1$smry[, "p value"])
```

We use Rcpp to estimate the mean of x variables.
```{r}
lrm(y, x, Rcpp = T)
```

Test our function with original R functions.
```{r}
library(testthat)
# beta
test_that("mlrmodel works", {
  expect_equal(round(as.numeric(lrm(y, x)$smry[, "beta"]), 3), round(summary(lm(y ~ x1 + x2 + x3))$coefficients[, "Estimate"], 3),
               check.attributes = FALSE)
})
# Rcpp
test_that("mlrmodel works", {
  expect_equal(round(as.numeric(lrm(y, x, Rcpp = T)), 3), round(colMeans(x), 3),
               check.attributes = FALSE)
})
```

We use benchmarks to test the efficiency of our new function.
```{r}
library(bench)
effct_func <- bench::mark(myfunc = {
  beta_my <- as.vector(round(as.numeric(lrm(y, x)$smry[, "beta"]), 3))
}, lmfunc = {
   beta_lm <- as.vector(round(summary(lm(y ~ x1 + x2 + x3))$coefficients[, "Estimate"], 3))
})
summary(effct_func)
```

We use benchmarks to test the efficiency of our Rcpp.
```{r}
effct_func_new <- bench::mark(rcppfunc = {
  mean_my <- as.vector(round(as.numeric(lrm(y, x, Rcpp = T)), 3))
}, orginfunc = {
   mean_og <- as.vector(round(colMeans(x), 3))
})
summary(effct_func_new)
```

